Discovering constraints in spreadsheets and tabular data

### 2016-09-08 Paper/ECAI/tabular.tex
Finished first version runtime analysis

These experiments, however, also show that the running time for various non-aggregate constraints increases as the size of blocks becomes very small.
Since these constraints have single vector arguments the block size should not have a strong effect.
However, in practice, for very small blocks to the superblock assignment phase has to generate a very large number of combinations, while for larger blocks this work is done mostly during the subassignment generation phase.
Since this last phase is more adept at generating these combinations, shifting this workload to the assignment phase slows down the algorithm.

>>>>

These experiments, however, also show that the running time for various non-aggregate constraints increases as the size of blocks becomes very small.
Since these constraints have single vector arguments the block size should not have a strong effect.
However, in practice, for very small blocks the superblock assignment phase has to generate a very large number of combinations, while for larger blocks this work is done mostly during the subassignment generation phase.
Since the implementation of that last phase is more adept at generating these combinations, shifting this workload to the assignment phase slows down the algorithm.
